\input{base}

\firstname{Jean-Marie}
\familyname{Comets}
\title{2nd year engineering student / Developer}
\address{13 rue Spréafico}{69100 Villeurbanne}
\mobile{(+33)6 99 65 94 07}
\email{jean.marie.comets@gmail.com}
\homepage{jmcomets.com}

\begin{document}
\maketitle

\section{Studies}

\cventry{2010 -- today}{Engineering -- Computer science}{INSA Lyon}{}{France}{}
\cventry{2010}{"Baccalauréat" obtained with honours}{}{France}{}{}
\cventry{2007 -- 2008}{Exchange class}{Cy-Fair High School}{Texas}{USA}{}

\section{Experience}

\cventry{June -- September 2013}{C++ developer}{LIRIS --
    CNRS}{Villeurbanne}{France}{Implemented a thickness diagram based on the
    exact arrangement of 3D balls. Built a front-end interface based on
    Qt/QGLViewer/GLUT, using extensive compiling and project tools
    (CMake/QMake).}

\cventry{July -- August 2012}{Entry assistant/Sysadmin helper}{ITEC
    Services}{Cenon}{France}{Helped enter diabetic patients' responses for a
    special study.\\Wrote script managing machines over the company's network.}

\cventry{September 2012 -- today}{CinéClub INSA
    association}{}{Villeurbanne}{France}{Current secretary. CinéClub INSA is
    the official student association of INSA Lyon who handles \textbf{legal}
    movie projections for the school's students.}

\cventry{September 2012 -- January 2014}{JeuxVidéo@INSA
    association}{}{Villeurbanne}{France}{Secretary for one year, president for
    the second. The JeuxVidéo@INSA association aims to promote video game
    creation (design, development, storyline, etc...). It organises meetings
    with video game professionals, conferences (notably with Ubisoft) and
    development events (Game Rush -- hackathons).}

%\cventry{March 2011 -- February 2012}{Sponsoring/Partners}{Gala INSA
    %Lyon}{Villeurbanne}{France}{Organized the school's Gala, notably by finding
    %sponsors for the event; at the head of a team of 3, in a complete team of
    %35.}

\section{Projects}

%\cventry{February -- April 2014}{twitto-feels}{}{}{}{School project.
    %Sentiment analysis on a given timeline, using Twitter's API.}

\cventry{December -- February 2014}{KHome}{}{}{}{School project.
    "Intelligent Home" modular system, built alongside an app store and a
    process communication system resembling JSON-RPC.}

\cventry{January 2014}{MindBlast}{}{}{}{Web app integrated to
    Salesforce aiming to provide suggestions to AXA sales employees. 4th
    place at a AXA/Salesforce hackthon organized by BeMyApp.}

\cventry{September 2013}{TESS}{}{}{}{Built a search engine based
    on model indexing (Scikit-learn, Elastic Search, Flask). 1st place
    at a \href{http://www.fhacktory.com}{FHacktory} hackathon.}.

\cventry{July -- September 2013}{IntoSpectrum}{}{}{}{Developing
    an server-sided audio-player with a web front-end using NodeJS.}

\cventry{December 2011 -- June 2012}{BdEContact}{}{}{}{Developed a
    web-based CRM for the school's student association (BdE). Built
    \textit{from scratch} in PHP/MySQL with a AJAX-based user interface.}

%\cventry{December 2012 -- May 2013}{EUSDAB}{}{}{Developed a
    %fighting-platform game in C++11 using SFML, Boost and CMake \\(Super Smash
    %Bros.-like)}

%\cventry{June 2011 -- December 2013}{jmc-consultant}{}{}{}{Built
    %from-scratch a website in PHP with a custom design.}

\textit{Note: most of these, as well as others, are open-source and available on
    \href{https://github.com/jmcomets}{Github}.}

\section{Computer science/Programming}

\cvcomputer{Web}{Python (Django, Flask), JavaScript (server: ExpressJS; client:
    JQuery, AngularJS), Ruby (Rails basics), PHP}{Database engines}{Oracle,
    MySQL, \\SQLite, MongoDB}
\cvcomputer{OOP}{C++, Python, Java, JavaScript (NodeJS)}{Imperative}{C,
    Pascal}
\cvcomputer{Tools}{Git, SVN, QMake, CMake}{Misc}{UML, Vim, Shell, \\\LaTeX.}

\section{Languages}

\cvlanguage{English}{mother tongue}{}
\cvlanguage{French}{bilingual}{}
\cvlanguage{Spanish}{good understanding and communicating}{}

\end{document}
